% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Patrick Ear \linebreak\normalsize{Graduate in January 2018}}
\address{7 Rue Beethoven \linebreak 94400 Vitry Sur Seine, France \linebreak \textbf{Already have J-1 VISA Sponsorship}}
\contacts{(+33) 6-78-71-02-12 \linebreak patrick.ear@epita.fr \linebreak linkedin.com/in/earpatrick \linebreak github.com/MonPote}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer, Co-Founder}{Kideep SAS}{Jan 2017 -- Jun 2017}
\raggedright Hexplore (www.hexplore.net \sim 40 concurrent users) is a web-application that help traveler to plan their trips. React, MeteorJS, MongoDB
			\begin{itemize}
				\item Reduced time to create a new point of interest by 80\% by creating a tool that find and fill most of the data in the form automatically and optimise the UI for the user.
				\item Designed and implemented the selection part of the web-application.
				\item Reduced the size of the images up to 90\% for each dimensions in order to speed up the page loading.
				\item Set up the continuous integration with Gitlab CI, Docker and AWS to safely deploy to production at least twice per day.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Web developer, Intern}{AppTask Limited}{Sep 2015 -- Jan 2016}	
\raggedright Cucsis (www.cucsis.com) is the new website of a swimming club in Hong Kong. \linebreak Laravel, MySQL, jQuery.		
			\begin{itemize}
				\item Rewrote admin and teacher views in PHP from Visual Basic, .NET and MSSQL.
				\item Implemented the generation of the reports and bills in PDF format with mPDF.
				\item Translated nested MSSQL queries to MySQL.
				\item Refactored the 10\% (\sim 8k lines) most duplicate code in the web-application.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Kremlin Bicetre, France}{EPITA Engineering School}{Sep 2012 -- Jan 2018}
		Specialization in Information System and Software Engineering
			\begin{itemize}
				\item Coursework : Cloud Architecture; Software Architecture; Object-Oriented Programming; Putting Agile Software Development Into Practice; Information System Urbanization; Vitualization
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Online}{Startup School by Y Combinator}{Apr 2017 -- Jun 2017}
		Weekly mentored by Y Combinator alumni
			\begin{itemize}
				\item Coursework: How and Why to Start A Startup; How to Get Ideas and How to Measure; How to Build a Product; How to Get Users and Grow; How to Invent the Future; How to Find Product Market Fit.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Beijing, China}{Beijing JiaoTong University}{Feb 2014 -- Jul 2014}
			Undergraduate exchange semester in Software Engineering major
			\begin{itemize}
				\item Coursework: Software Foundations; Computer Architecture; Calculus I \& II; Operating System; Java; Databases.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{MyStockNotif} (2017). Android and iOS application that send notification to the user when a chosen stock reaches a threshold. Javascript, React Native
				\item \textbf{Smart Cardio T-shirt} (2017). Android application link to a Raspberry Pi and sensor that enable the detection of heart diseases like tachycardia and bradycardia. Java, Javascript, AWS IoT
				\item \textbf{FnacSimulator} (2016). Simulation of the information system of a french supermarket. 7 applications need to communicate together in real time and I was in charge of the cashier one. Java JEE, PostgresSQL
				\item \textbf{Tipz} (2016). A Patreon-like website made in pair-programming. Python, Javascript, PostgreSQL
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Javascript; Java; PHP; MongoDB; SQL 
				\item React; MeteorJS; Docker; AWS(EC2, EBS, S3, ELB); Git; Gitlab CI
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
